\documentclass[OPS,lsstdraft,authoryear,toc]{lsstdoc}
\input{meta}

% Package imports go here.

% Local commands go here.

%If you want glossaries
%\input{aglossary.tex}
%\makeglossaries

\title{The Rubin Observatory Target-of-Opportunity Mock Data Challenge}

% This can write metadata into the PDF.
% Update keywords and author information as necessary.
\hypersetup{
    pdftitle={The Rubin Observatory Target-of-Opportunity Mock Data Challenge},
    pdfauthor={Sean Patrick MacBride},
    pdfkeywords={}
}

% Optional subtitle
% \setDocSubtitle{A subtitle}

\input{authors}

\setDocRef{RTN-107}
\setDocUpstreamLocation{\url{https://github.com/lsst/rtn-107}}
\setDocDOI{10.71929/rubin/3010871}

\date{\vcsDate}

% Optional: name of the document's curator
% \setDocCurator{The Curator of this Document}

\setDocAbstract{%
We describe the activities of the Target-of-Opportunity mock data challenge, taking place from Sep 22 2025 - Oct 18 2025. We center this activity in four questions that are critical for maximizing the scientific output of the ToO system:
\begin{itemize}
    \item How quickly can Rubin Observatory start observing after a ToO alert is received?
    \item How efficient is Rubin Observatory at recovering the host of a ToO event?
    \item How accurate are the observing strategies that the community has created for the ToO program?
    \item How can expert ToO scientists interact effectively with the ToO system, where many processes are fully automated?
\end{itemize}
In this challenge, and the report summarized herein, we aim to answer the aforementioned questions to better the Rubin ToO program.
}

% Change history defined here.
% Order: oldest first.
% Fields: VERSION, DATE, DESCRIPTION, OWNER NAME.
% See LPM-51 for version number policy.
\setDocChangeRecord{%
  \addtohist{1}{2025-09-18}{Introduction + Abstract.}{MacBride}
  \addtohist{2}{2025-12-29}{Add DOI}{T.\ Jenness}
}



\begin{document}

% Create the title page.
\maketitle
% Frequently for a technote we do not want a title page  uncomment this to remove the title page and changelog.
% use \mkshorttitle to remove the extra pages

% ADD CONTENT HERE
% You can also use the \input command to include several content files.

\input{introduction}
\input{organization}
\input{activity}
\input{latency}
\input{efficiency}
\input{stratgen}
\input{human}
\input{conclusion}
\appendix

\section{Acknowledgements}

This material is based upon work supported in part by the National Science Foundation through Cooperative Agreements AST-1258333 and AST-2241526 and Cooperative Support Agreements AST-1202910 and AST-2211468 managed by the Association of Universities for Research in Astronomy (AURA), and the Department of Energy under Contract No.\ DE-AC02-76SF00515 with the SLAC National Accelerator Laboratory managed by Stanford University.
Additional Rubin Observatory funding comes from private donations, grants to universities, and in-kind support from LSST-DA Institutional Members.

% Include all the relevant bib files.
% https://lsst-texmf.lsst.io/lsstdoc.html#bibliographies
\section{References} \label{sec:bib}
\renewcommand{\refname}{} % Suppress default Bibliography section
\bibliography{local,lsst,lsst-dm,refs_ads,refs,books}

% Make sure lsst-texmf/bin/generateAcronyms.py is in your path
\section{Acronyms} \label{sec:acronyms}
\input{acronyms.tex}
% If you want glossary uncomment below -- comment out the two lines above
%\printglossaries





\end{document}
